### 2015-06-20 Manuscript/Table_results.tex
Table result
supplementary figures (updated)

% Fri Jun  5 15:29:14 2015

@@

  Afrosoricida & species & 23/42 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar3.pdf} & 1.55 & -2.32 \\ 
  Carnivora & family & 11/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar4.pdf} & 0.52 & 1.6 \\ 
  \textbf{Carnivora} & \textbf{genus} & \textbf{30/125} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar5.pdf} & \textbf{4.01**} & \textbf{1.75*} \\ 
  \textbf{Carnivora} & \textbf{species} & \textbf{42/283} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar6.pdf} & \textbf{17.95**} & \textbf{3.1**} \\ 
  Cetartiodactyla & family & 20/21 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar7.pdf} & 0.35 & 1.11 \\ 
  Cetartiodactyla & genus & 76/128 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar8.pdf} & -3.22 & -1.12 \\ 
  Cetartiodactyla & species & 106/311 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar9.pdf} & -2.77 & -2.1 \\ 
  Chiroptera & family & 13/18 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar10.pdf} & 0.87 & 0.65 \\ 
  \textbf{Chiroptera} & \textbf{genus} & \textbf{68/202} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar11.pdf} & \textbf{18.87**} & \textbf{1.09} \\ 
  \textbf{Chiroptera} & \textbf{species} & \textbf{108/1054} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar12.pdf} & \textbf{20.11**} & \textbf{2.24*} \\ 

@@

  Cingulata & genus & 8/9 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar14.pdf} & 1.31 & -1.66 \\ 
  Cingulata & species & 6/25 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar15.pdf} & 0.65 & -0.47 \\ 

@@

  Dasyuromorphia & genus & 7/22 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar17.pdf} & -1.1 & -1.78 \\ 
  Dasyuromorphia & species & 8/64 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar18.pdf} & -1.1 & -1.31 \\ 

@@

  Didelphimorphia & species & 40/84 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar24.pdf} & -1.33 & -1.7 \\ 
  Diprotodontia & family & 9/11 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar25.pdf} & -0.35 & 1.11 \\ 
  Diprotodontia & genus & 20/38 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar26.pdf} & -0.31 & -1.57 \\ 
  Diprotodontia & species & 16/126 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar27.pdf} & -0.98 & -2.6 \\ 

@@

  Erinaceomorpha & species & 21/22 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar30.pdf} & -0.78 & -0.19 \\ 

@@

  Macroscelidea & species & 5/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar39.pdf} & -0.47 & -0.89 \\ 

@@

  Monotremata & genus & 2/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar44.pdf} & -0.7 & -0.71 \\ 
  Monotremata & species & 2/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar45.pdf} & -0.97 & -1.01 \\ 

@@

  Paucituberculata & genus & 2/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar50.pdf} & -0.76 & -0.74 \\ 

@@

  Peramelemorphia & species & 16/18 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar54.pdf} & -0.55 & 0.49 \\ 

@@

  Perissodactyla & species & 7/16 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar57.pdf} & 0.73 & -2.63 \\ 

@@

  Pholidota & species & 3/8 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar60.pdf} & 1.14 & 0.66 \\ 
  Pilosa & family & 3/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar61.pdf} & -0.6 & -0.85 \\ 
  Pilosa & genus & 3/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar62.pdf} & -0.88 & -1.09 \\ 
  Pilosa & species & 3/29 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar63.pdf} & -1.51 & -1.47 \\ 

@@

  Primates & genus & 48/68 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar65.pdf} & -0.3 & -1.29 \\ 
  Primates & species & 56/351 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar66.pdf} & -1.5 & -2.18 \\ 

@@

  Rodentia & family & 10/32 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar70.pdf} & 0.11 & -0.3 \\ 
  Rodentia & genus & 20/451 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar71.pdf} & -1.03 & 0.71 \\ 
  Rodentia & species & 10/2095 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar72.pdf} & -0.97 & -1.75 \\ 

@@

  Scandentia & genus & 2/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar74.pdf} & -0.75 & -0.76 \\ 
  Scandentia & species & 2/20 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar75.pdf} & -1.26 & -1.27 \\ 

@@

  Sirenia & species & 2/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar78.pdf} & -0.96 & -0.94 \\ 
  Soricomorpha & family & 3/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar79.pdf} & -0.95 & -1.05 \\ 
  Soricomorpha & genus & 19/43 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar80.pdf} & 1.16 & -1.01 \\ 
  Soricomorpha & species & 19/392 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar81.pdf} & -1.87 & -3.09 \\ 

>>>>

% Sat Jun 20 17:41:32 2015

@@

  \textbf{Afrosoricida} & \textbf{species} & \textbf{23/42} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar3.pdf} & \textbf{1.89*} & \textbf{1.19} \\ 
  Carnivora & family & 11/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar4.pdf} & 0.43 & 1.68 \\ 
  \textbf{Carnivora} & \textbf{genus} & \textbf{30/125} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar5.pdf} & \textbf{4.14**} & \textbf{1.81*} \\ 
  \textbf{Carnivora} & \textbf{species} & \textbf{42/283} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar6.pdf} & \textbf{18.64**} & \textbf{3.02**} \\ 
  Cetartiodactyla & family & 21/21 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar7.pdf} &   &   \\ 
  \textbf{Cetartiodactyla} & \textbf{genus} & \textbf{77/128} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar8.pdf} & \textbf{0.87} & \textbf{1.77*} \\ 
  \textbf{Cetartiodactyla} & \textbf{species} & \textbf{129/310} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar9.pdf} & \textbf{2.72*} & \textbf{0.04} \\ 
  Chiroptera & family & 13/18 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar10.pdf} & 0.55 & 0.63 \\ 
  \textbf{Chiroptera} & \textbf{genus} & \textbf{85/202} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar11.pdf} & \textbf{16.91**} & \textbf{2.85**} \\ 
  \textbf{Chiroptera} & \textbf{species} & \textbf{165/1053} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar12.pdf} & \textbf{14.55**} & \textbf{3.44**} \\ 

@@

  Cingulata & genus & 8/9 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar14.pdf} & 1.49 & -1.63 \\ 
  Cingulata & species & 6/29 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar15.pdf} & 1.43 & 0.36 \\ 

@@

  Dasyuromorphia & genus & 7/22 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar17.pdf} & -1 & -1.45 \\ 
  Dasyuromorphia & species & 8/64 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar18.pdf} & -1.15 & -0.62 \\ 

@@

  Didelphimorphia & species & 40/84 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar24.pdf} & -0.94 & 0.36 \\ 
  Diprotodontia & family & 9/11 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar25.pdf} & -0.8 & 0.56 \\ 
  Diprotodontia & genus & 20/38 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar26.pdf} & -1.36 & -0.73 \\ 
  Diprotodontia & species & 16/126 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar27.pdf} & -2.29 & -1.55 \\ 

@@

  Erinaceomorpha & species & 21/22 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar30.pdf} & -1.1 & -0.3 \\ 

@@

  Macroscelidea & species & 5/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar39.pdf} & -0.98 & -1.38 \\ 

@@

  Monotremata & genus & 2/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar44.pdf} & -0.71 & -0.71 \\ 
  Monotremata & species & 2/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar45.pdf} & -1.01 & -1.03 \\ 

@@

  Paucituberculata & genus & 2/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar50.pdf} & 0 & 0 \\ 

@@

  Peramelemorphia & species & 16/18 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar54.pdf} & -0.09 & 1 \\ 

@@

  Perissodactyla & species & 7/16 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar57.pdf} & 0.62 & -2.5 \\ 

@@

  \textbf{Pholidota} & \textbf{species} & \textbf{3/8} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar60.pdf} & \textbf{2.64*} & \textbf{2.23*} \\ 
  Pilosa & family & 3/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar61.pdf} & 0.94 & 0.93 \\ 
  Pilosa & genus & 3/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar62.pdf} & -0.36 & -0.31 \\ 
  Pilosa & species & 3/29 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar63.pdf} & 0.33 & 0.79 \\ 

@@

  Primates & genus & 48/68 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar65.pdf} & -0.41 & -1.4 \\ 
  Primates & species & 56/351 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar66.pdf} & -1.6 & -2.04 \\ 

@@

  Rodentia & family & 11/32 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar70.pdf} & -0.46 & -1.91 \\ 
  Rodentia & genus & 21/450 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar71.pdf} & -2.11 & 0.3 \\ 
  Rodentia & species & 15/2094 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar72.pdf} & -1.65 & -2.55 \\ 

@@

  Scandentia & genus & 2/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar74.pdf} & -0.77 & -0.76 \\ 
  Scandentia & species & 2/20 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar75.pdf} & -1.79 & -1.99 \\ 

@@

  Sirenia & species & 4/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar78.pdf} &   &   \\ 
  Soricomorpha & family & 3/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar79.pdf} & -0.93 & -0.92 \\ 
  \textbf{Soricomorpha} & \textbf{genus} & \textbf{19/43} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar80.pdf} & \textbf{6.98**} & \textbf{2.49*} \\ 
  \textbf{Soricomorpha} & \textbf{species} & \textbf{19/392} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar81.pdf} & \textbf{13.19**} & \textbf{3.89**} \\ 
